Software Citation Principles

### 2016-06-24 sc-principles/software-citation-principles.tex
fixed Dan affiliation

\thanks{{}$^{1}$ GitHub, Inc., San Francisco, CA, USA}
\thanks{{}$^{2}$ National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois at Urbana--Champaign, Urbana, IL, USA}
\thanks{{}$^{3}$ School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University, Corvallis, OR, USA}

>>>>

\thanks{{}$^{1}$ GitHub, Inc., San Francisco, CA, USA}
\thanks{{}$^{2}$ National Center for Supercomputing Applications \& Electrical and Computer Engineering Department \& School of Information Sciences, University of Illinois at Urbana--Champaign, Urbana, IL, USA}
\thanks{{}$^{3}$ School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University, Corvallis, OR, USA}
